An Open System for\\ Managing Short Programming Exercises

### 2013-08-09 paper/talk.tex
emphasize difficulty of writing exercises
minor tweak
PCRS can import CloudCoder exercises!
current use?
authorship for PCRS paper

\begin{itemize}
  \item Many students struggle in introductory programming courses
  \item Mastery of basic concepts and techniques is essential for success
  \item Short programming exercises ({\it {\` a} la} CodingBat):
  \begin{itemize}
    \item Students write or complete a short (5-15 line) program
    \item Interface is typically web-based
    \item Correctness is judged with a series of test cases
    \item Student receives immediate feedback about results of tests
  \end{itemize}
  \item Exercises are useful for:
  \begin{itemize}
    \item Skills development
    \item Self-tests to accompany reading
    \item Extra practice
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
  \item Make programming exercises written by many people available
        for whatever uses are appropriate
  \begin{itemize}
    \item Our need: exercises to assign in the context of a course
    \item Related work: PCRS (Petersen et.\ al., SIGCSE 2013), in-class
          exercises to support peer instruction
    \item We can imagine lots of other uses: for example, Codecademy-style
          self-learning
  \end{itemize}
  \item Make the {\em sharing} of exercises a subject of research
  \begin{itemize}
    \item What kinds of exercises are most easily reused?
    \item How can exercises be classified and organized?
  \end{itemize}
\end{itemize}

@@

\begin{center}
\vskip -.15in
\includegraphics[width=4.5in]{images/screenshot4}
\end{center}

@@

\begin{itemize}
\item Pilot studies:
  \begin{itemize}
  \item Canisius College: 30 students, CS1, C++
  \item York College: 122 students, CS1, C
  \item Knox College: 23 students, CS1, Java
  \item U.\ of Auckland: 30 students, CS1, C
  \end{itemize}
\item Experiences:
  \begin{itemize}
  \item The software works, students seem to like it
  \item Writing exercises from scratch is hard
  \item Repository has 100+ exercises, but not much reuse has occurred yet
  \end{itemize}
\item Can we scale it to larger courses?
  \begin{itemize}
\item September 2013: U.\ of Auckland: 700 students, CS1, C
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item Are short exercises useful?
  \begin{itemize}
  \item Would {\em you} want to use short exercises in your course?
  \item What experiments should we do to measure effect on outcomes?
  \end{itemize}
\item How do we most effectively incorporate short exercises into a course?
  \begin{itemize}
  \item How do we know what exercises should be assigned?
  \item In what order should the exercises be assigned?
  \item What mix of short exercises vs.\ larger assignments?
  \end{itemize}
\end{itemize}

>>>>

\begin{itemize}
  \item Many students struggle in introductory programming courses
  \item Mastery of basic concepts and techniques is essential for success
  \item Short programming exercises ({\it {\` a} la} CodingBat):
  \begin{itemize}
    \item Students write or complete a short (5-15 line) program
    \item Interface is typically web-based
    \item Correctness is judged with a series of test cases
    \item Student receives immediate feedback
  \end{itemize}
  \item Exercises are useful for:
  \begin{itemize}
    \item Skills development
    \item Self-tests to accompany reading
    \item Extra practice
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
  \item Make programming exercises written by many people available
        for whatever uses are appropriate
  \begin{itemize}
    \item Our need: exercises to assign in the context of a course
    \item Related work: PCRS (Zingaro et.\ al., SIGCSE 2013), in-class
          exercises to support peer instruction
      \begin{itemize}
      \item Summer 2013: PCRS can import exercises from the CloudCoder exercise repository!
      \end{itemize}
    \item We can imagine lots of other uses: for example, Codecademy-style
          self-learning
  \end{itemize}
  \item Make the {\em sharing} of exercises a subject of research
  \begin{itemize}
    \item What kinds of exercises are most easily reused?
    \item How can exercises be classified and organized?
  \end{itemize}
\end{itemize}

@@

\begin{center}
\vskip -.15in
\includegraphics[width=4.5in]{images/screenshot5}
\end{center}

@@

\begin{itemize}
\item Pilot studies:
  \begin{itemize}
  \item Canisius College: 30 students, CS1, C++
  \item York College: 122 students, CS1, C
  \item Knox College: 23 students, CS1, Java
  \item U.\ of Auckland: 30 students, CS1, C
  \end{itemize}
\item Experiences:
  \begin{itemize}
  \item The software works, students seem to like it
  \item Writing exercises from scratch is hard!
  \item Repository has 100+ exercises, but not much reuse has occurred yet
  \end{itemize}
\item Can we scale it to larger courses?
  \begin{itemize}
\item September 2013: U.\ of Auckland: 700 students, CS1, C
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item Are short exercises useful?
  \begin{itemize}
  \item Do you use short exercises in your courses currently?
  \item Would {\em you} want to use short exercises in your course?
  \item What experiments should we do to measure effect on outcomes?
  \end{itemize}
\item How do we most effectively incorporate short exercises into a course?
  \begin{itemize}
  \item How do we know what exercises should be assigned?
  \item In what order should the exercises be assigned?
  \item What mix of short exercises vs.\ larger assignments?
  \end{itemize}
\end{itemize}
